Response to reviewer comments ELE-00738-2016

### 2017-02-24 paper/EL-reviewer-comments-1.Rmd
Add responses to Reviewer #1

    *We revised the text to better reflect the contribution of @Tylianakis2010 at the same time we added a reference to a more recent paper by @Kaiser-Bunbury2015 who explicitly deals with oportunities, limitations and implications of applying network metrics in conservation science.*

@@

    *Thanks to this comment and those from other reviewers have helped us identify some shortcomming on the way we were introducing the control framework in the paper. We have largely rewritten the 'Theoretical framework' section and we start by offering a brief overview of control theory which emphasize on a dynamical perspective to complex networks (Line XXX). We then follow with a paragraph devoted to how structural controlability is unable to provide information about the particulars of the control signal and the feasibility of its application (Line XXX). Without disregard the usefulness of the proposed approach, we also mention in this paragraph, and later on the discussion (Line XXX), how recently developed numerical methods [@Cornelius2013] might offer exiting results in this regard.*

@@

    *Thanks for pointing this out. In fact we thoroughly implememnted the approach of [@Ruths2014] at initial stages of the project. However we found that the profile of the network depends to an extreme degree on the chosen link directionality and very little on the particulars of a given network. Because of that reason we decided to exclude this approach altogether from the final draft. Nevertheless, due to this comment and one of Referee 2 we included this treatment in the Supplementary Materials Section XX and reference it briefly in the manuscript (Line XXX). In SM SectionXX we explain that because we focus on bipartite networks, cycles only appear, and in fact dominate, when we consider the case of bidirectional links. We are particularly grateful for the reference to @Motter2015. We were unaware of this paper and has been extremely useful to contextualise our work in the broader control theory.*

@@

    *Indeed most of the literature treats the problem of controlability on unweighted networks. It has been shown, however, at least in pollination networks like the ones used in our paper, that the interaction weights carry important information about the patterns and processes in the community. In the paper we use the visitation weights directly or indirectly in two different aspects. First, we use them to determine the direction of control (via the dependence asymetry). Second, which directly adresses the reviewer's comment, we use it to give priority to matchings that have the largest weight, which potentially also have the largest impact on the network state for a given management intervention. Because the weights determine to some extent the dynamical relationships between species, our approach attempt to incorporate more realism to the structural controllability approach. We acknoweledge our presentation was confusing, especially for readers familiar wit the control literature, and therefore have added a whole paragraph in the method describing our rationale (Lines XXX)*

- When defining n_d on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.

    *We have rewritten that section and the equivalent sentence now reads "It has been shown that a particular network that can be expressed as a state space system of the form $\dot{x} = Ax + Bu(t)$ is controllable if there exists a minimum number of nodes in the network (N~D~ > 0) to which is possible to aply an external control signal that propagates trough the network to in turn drive the state of every other node in the network to a particular configuration [@Kalman1963; @Liu2011]."*

@@

    *We are sorry for the impresicion. It should have been "all possible maximum cardinality matchings". In any case, because of the suggestion about the driver species concept we have decided to remove this sentence. We also reworded the text in Lines XXX to clarify why our approach to identify species importance is not exclsively centered on maximum matchings.*

@@

    *Thanks to this suggestion and those of other reviewers, we have made important changes to Figure 1. On it we include a better ilustration of our methodology for a simple network while paying special effort to bring clarity to the different node categories as superior, matched and unmatched nodes. TO DO*

@@

    *Overall our choice of terminology was poor. We have eliminated the term "driver species" from the manuscript and now just mention, in the referee's words, how the frequency with which species exist on key paths trough the network provides indication of their relative importance.*

@@

    *Thanks for pointing this out. As suggested, we have included a figure that help explains our method to compute all possible maximum cardinality matchings. However because the methodology itself is not one of our main contributions and because of space limitations we have included that figure in the Supplementary Material. TO DO.*

@@

    *We apologise for the poor choice of words. As the referee points out it is not an estimation but an exact calculation. The sentence now reads "To do so, we calculated the maximum matching of the corresponding pollination network, and determined the minimum proportion of species that need directed interventions to fully control the species abundances in the community".*

@@

    *Thanks for the observation. We have now included the number of interactions in the network as an extra explanatory variable. TO DO*

@@

    *In retrospect we realise that we did not have a clear rationale to include an randomisation of the link weights. As the referee points out, a change on the weights would only be reflected on a potential change on the interaction asymmetry. We identifyed two problems with this approach: first the changes aren't easily tractable, and second there is not a standard way to randomise weight in quantiative networks and the particular choice of the algorithm might influence the results. We therefore decided to remove the null model that maintained the degree of species and randomised the weight of the links as the effect of the asymetry is explicitly tackled by the second approach in which we maintain the structure but randomise the asymmetry.*

@@

Indeed, in the Discussion the authors say for example, "Because of their effects on other species in the community, driver species might be natural candidates for management interventions." This may be true, but it seems to me that the role of the directly-controlled species (that populate n_d), which serve as the gateway for the control signals to the rest of the network, merits discussion here as well. How are the two related? Do the authors envision a scenario where a control signal is actually being sent in to the network? Or do they rather envision a scenario where no controls are being used (which is counter to the central idea of structural controllability), and are they instead identifying these drivers nodes simply to provide a proxy measure of the effect of node state perturbations on the rest of the network? The latter seems more plausible than the former, but in any case more detail is needed.

@@

@@

Minor comments
Line  236: there is a missing period.

@@

This manuscript proposes to apply the methods published in previous papers (e.g. Liu et al, Nature 2011) on the controllability of complex systems to invaded pollination networks. Note that controllability is rebranded “manageability” (unless it has a different meaning in this paper?). The manuscript also proposes to identify the nodes to manage or driver species. This is a fascinating area of research.
Performing a controllability study on ten pairs of uninvaded and invaded plant-pollinator networks, the main finding is that invaded networks require a higher number of nodes to control than their non-invaded counterpart and invasive plants were driver species in all studied communities.
The study is scientifically sound. However the manuscript is dense and difficult to read. In particular the section Theoretical framework and its subsection are confusing and should be merged with the Methods section. The discussion should be strengthen.
In its current form, it is unlikely that readers will be able to understand or replicate the research presented – which is a shame considering the authors went through a lot of trouble to apply a control theory study in an ecological context. An overall simplification of the language/sentences and jargon used will increase the readability of this manuscript. Ruths (2014, Science) and Liu (2011, Nature) are doing a better job at explaining maximum matching, driver nodes and the overall challenge of controllability.

@@

>>>>

    *We have now revised the text to better reflect the contribution of @Tylianakis2010. At the same time, we added a reference to a more recent paper by @Kaiser-Bunbury2015 that explicitly deals with opportunities, limitations and implications of applying network metrics in conservation science.*

@@

    *Thanks to this comment and those from other reviewers have helped us identify some shortcomings on the way we were introducing the control framework in the paper. We have largely rewritten the 'Theoretical framework' section. We start by offering a brief overview of control theory. In this overview, we emphasise our assumptions regarding the dynamical nature of the interactions. And follow with a brief discussion that indicates how structural controllability is unable to provide information about the particulars of the control signal and the feasibility of its application. Without disregard the usefulness of the proposed approach, we also mention at the end of the discussion how recently developed numerical methods [@Cornelius2013] might offer exciting results in this regard.*

@@

    *Thanks for pointing this out. In fact, we explored the implementation of the approach of [@Ruths2014] at initial stages of the project. However we decided to exclude this approach from the final draft, mainly due to space limitations. Nevertheless, due to this comment and one of Referee 2 we have rediscovered its value and use it to support our decision to include the analysis of superior nodes, and not just driver nodes, in our manuscript. We now dedicate a whole section in the Supporting Information (S2). In summary, we found our networks weighted by asymmetry to be external dilation dominated, and hence have only a small number of cycles. Networks weighted by mutual dependences are dominated by cycles and hence challenging to our approach. In another section in the Supporting Information (S6) we discuss the implications that using these networks have, and our approach to circumvent them. Finally we are grateful for the reference to @Motter2015. We were unaware of this paper and it has been extremely useful to contextualise our work in the broader control theory literature.*

@@

    *Indeed most of the literature treats the problem of controlability on unweighted/binary networks. In that special case maximum matchings are equivalent to maximum cardinality matchings. It has been shown, however, that the interaction weights carry important information in pollination networks about the patterns and processes in the community. In the paper we use the visitation weights directly or indirectly in two different ways. First, we use them to determine the potential direction of control (via the dependence asymmetry). Second—which directly adresses the reviewer's comment—we use them to give priority to matchings that have the largest weight since these arguably have the largest impact on the network state for a given management intervention. Because the weights determine to some extent the dynamical relationships between species, our approach attempts to incorporate more ecological realism to the structural controllability approach. We acknoweledge our earlier presentation of this rationale was confusing, especially for readers familiar with the control literature, and therefore have added a whole paragraph describing our rationale in the "Relative importance" subsection in the "Theoretical frameowrk". To minimise potential confusions we are more careful when introducing each of these concepts, and have added—as suggested by the reviewer—a glossary for easy reference.*

- When defining *n~d~* on line 119, it is more accurate to say that it is the "minimum number" of species needed to gain full control.

    *We have completely rewritten that section and the equivalent sentence now reads "Conveniently, in a network with linear dynamics, the information necessary to determine the minimum number of driver nodes D is fully contained in the network structure..."*

@@

    *We are sorry for the imprecision. It should have been "all possible maximum cardinality matchings". In any case, because of the reviewers' suggestion about the driver species concept we have now removed this sentence. We hope that the new text we have included on the "Relative importance" subsections, both in the "Theoretical framework" and "Empirical application", and in Supporting Information S7, helps clarify why our approach to identify species importance is not exclusively centred on maximum matchings.*

@@

    *Thanks to this suggestion and those of other reviewers, we have made important changes to Figure 1. In it, we include a better illustration of our methodology for a simple network while paying special effort to bring clarity to the different node categories as superior, driver, matched, and unmatched nodes. We hope the figure, in addition to our new introduction to the elements of a maximum matching, make the concept easier to understand.*

@@

    *We agree that in hindsight, our choice of terminology was poor. We have eliminated the term "driver species", which had a different meaning to the usual concept of "control node", from the manuscript. Now, we stick to the terminology that is already used, and refrain for introducing a new term for the species that are classified as superior nodes in all possible control strategies.*

@@

    *Thanks for pointing this out. As suggested, we have included a figure that help explains our method to compute all possible maximum cardinality matchings. Nevertheless, because of space limitation, and because the methodology itself is not one of our main contributions, we have included the procedure and the figure in the Supporting Information (S1 and Figure S2).*

@@

    *We again apologise for the poor choice of words. As the referee points out it, this is not an estimation but an exact calculation. The sentence now reads "To do so, we calculated the maximum matching of the corresponding pollination network, and determined the minimum proportion of species that need directed interventions to fully control the species abundances in the community".*

@@

    *Thanks for the observation. We have now included the network connectance as an extra explanatory variable. We included connectance (link density) and not the number of links, because it allows comparisons across multiple networks of differing size. We found it to have a negative and moderate relationship with the density of driver nodes.*

@@

    *In retrospect we realise that our rationale to include a randomisation of the link weights was not clear enough. As the referee points out, a change on the weights would only be reflected on a potential change on the interaction asymmetry. We identifyed two problems with this approach: first the changes aren't easily tractable, and second there is not a standard way to randomise weight in quantiative networks and the particular choice of the algorithm might influence the results. We therefore decided to remove the null model that maintained the degree of species and randomised the weight of the links as the effect of the asymmetry is explicitly tackled by the second approach in which we maintain the structure but randomise the asymmetry.*

@@

    *Thanks for the suggestion. In the methods, where we describe the empirical application, we now state the minimum, maximum, and the mean number of species for both the networks from Bristol, UK and Cap de Creus, Spain. In addition, now we briefly discuss the proportion of driver nodes we found in the studied pollination networks in the fourth paragraph of the Discussion. We do so, in the context of highlighting the potential caveats of one of our metrics of species importance.*

- Indeed, in the Discussion the authors say for example, "Because of their effects on other species in the community, driver species might be natural candidates for management interventions." This may be true, but it seems to me that the role of the directly-controlled species (that populate n_d), which serve as the gateway for the control signals to the rest of the network, merits discussion here as well. How are the two related? Do the authors envision a scenario where a control signal is actually being sent in to the network? Or do they rather envision a scenario where no controls are being used (which is counter to the central idea of structural controllability), and are they instead identifying these drivers nodes simply to provide a proxy measure of the effect of node state perturbations on the rest of the network? The latter seems more plausible than the former, but in any case more detail is needed.

    *Agreed. Given that driver nodes have received a considerable amount of attention in the control literature, we realise that neglecting them might be confusing, especially for readers familiar with control theory. We have fully incorporated this suggestion and our paper is now much more comprehensive. Now, to determine the potential importance of a species, we determine, not only its properties as a superior node, but also its properties as a driver node. We have dedicated a large proportion of the discussion to discuss the advantages and limitations of each of them and how they relate to each other and to realistic management applications. To do build this discussion we harnessed results from additional modelling analysis in the main text, as well as the lessons learned from the application of the @Ruths2014 control profiles approach.*

@@

    *We have now included a subpanel in Figure 3 that depicts the distribution of _n~D~_ for our empirical networks. The adjusted values were merely partial residuals of the fitted statistical models. We therefore have changed the axis titles to reflect this fact and avoid confusion.*

@@

    *This was a mistake on our part. We were not interested in determining whether the __absolute__ value of n~D~ differs among approaches, but instead, we wanted to determine wether the __relative__ values showed agreement. This is, our primary concern was to test whether networks with a high n~D~ under the asymmetry weighting also had a high n~D~ under the bidirectional dependences weighting. We have changed the text in the Supporting Information (S6) to improve clarity.*

- Minor comments. Line  236: there is a missing period.

    *Thanks for pointing it out. We have added the period.*

@@

This manuscript proposes to apply the methods published in previous papers (e.g. Liu et al, Nature 2011) on the controllability of complex systems to invaded pollination networks. Note that controllability is rebranded “manageability” (unless it has a different meaning in this paper?). The manuscript also proposes to identify the nodes to manage or driver species. This is a fascinating area of research.

Performing a controllability study on ten pairs of uninvaded and invaded plant-pollinator networks, the main finding is that invaded networks require a higher number of nodes to control than their non-invaded counterpart and invasive plants were driver species in all studied communities.
The study is scientifically sound. However the manuscript is dense and difficult to read. In particular the section Theoretical framework and its subsection are confusing and should be merged with the Methods section. The discussion should be strengthen.

In its current form, it is unlikely that readers will be able to understand or replicate the research presented – which is a shame considering the authors went through a lot of trouble to apply a control theory study in an ecological context. An overall simplification of the language/sentences and jargon used will increase the readability of this manuscript. Ruths (2014, Science) and Liu (2011, Nature) are doing a better job at explaining maximum matching, driver nodes and the overall challenge of controllability.

@@

    *Thanks for pointing it out. Given the tight 150 word limit imposed by the Journal, we had some trouble highlighting the novelty of the approach while maintaining important details about the empirical application. We hope the current version of the abstract shows substantial improvement.*
